What can Stack Traces tell us about Java Exceptions?

### 2014-08-19 java-stacks.tex
This version of the paper discuss the results starting from Java.

@@

@@

\begin{figure}
\centering
%\includegraphics[width=\hsize]{chart_exceptiontypes.pdf}
\includegraphics[width=\hsize]{exception_types.pdf}
\caption{Distribution of Checked and Unchedked exceptions.}
\label{fig:typeroot}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{llll}
    \hline
    \bfseries{Wrapper Type} & \bfseries{Root Cause} & \bfseries{Occurrences} & \bfseries{Projects} \\
    \hline
      none   & Runtime   &  2360 & 359 \\
      none  &   Checked  & 422  & 117 \\
      none  &   Error   & 381  & 141 \\
      none &  Undefined  &  15   & 10  \\
      none & Throwable  &  1    & 1 \\
     \hline
      Runtime   & Runtime & 560  & 182 \\    
      Checked   & Checked & 98   & 42  \\
      Error     & Error   & 15   & 14  \\
    \hline
      Runtime &  Checked   & 114  & 70  \\
      Runtime   &  Error   & 57   & 38  \\
      Checked &  Runtime   & 22   & 12  \\
      Checked & Error    &  8    & 7 \\
      Error & Checked     &  7    & 4 \\
      Error & Runtime     &  13   & 6 \\
      Throwable & Runtime &  3    & 1 \\
      Undefined & Runtime &  3    & 3 \\
      Undefined & Error &  1    & 1 \\
    \hline
  \end{tabular}
\caption{Kinds of wrappings found on the stacks of 482 ANDROID projects found on Github}
\label{tab:wrappingandroid}
\end{table}

@@

ANDROID	 \- 66
APP	\- 29 	(HOW MANY?? AND WHICH??)
LIB  \- 19 (HOW MANY AND WHICH?)

@@

android.app.ActivityThread \- 47
android.view.LayoutInflater \- 7
org.gege.caldavsyncadapter.syncadapter.SyncAdapter \- 7
org.springframework.web.client.RestTemplate \- 6
android.os.AsyncTask \- 5

Code snipet:

android.app.ActivityThread.

public final Activity startActivityNow(...) \{
...
return performLaunchActivity(r, null);
\}

private Activity performLaunchActivity(...) \{
try \{
.....
\} catch (Exception e) {
..
throw new RuntimeException(
"Unable to instantiate activity " + component
+ ": " + e.toString(), e);
..
\}
\}

@@

(java.lang.RuntimeException,java.lang.ClassNotFoundException)	32
(java.lang.RuntimeException,java.lang.NoSuchMethodException)	6
(java.lang.RuntimeException,java.lang.InstantiationException)	5
(com.github.andlyticsproject.console.NetworkException,org.apache.http.client.HttpResponseException)	5
(android.view.InflateException,java.lang.NoSuchMethodException)	4

java.lang.RuntimeException	69 \- 61%
android.view.InflateException	10 \- 8,7%
com.github.andlyticsproject.console.NetworkException	7
java.lang.IllegalStateException	6
org.springframework.web.client.ResourceAccessException	6
com.github.andlyticsproject.console.DevConsoleProtocolException	3

@@

ANDROID	50
LIB 	6
APP	1

android.os.AsyncTask \-	25
android.app.ActivityThread \- 15
android.view.LayoutInflater \- 7
org.asynctasktex.AsyncTaskExd \- 3
android.support.v4.content.ModernAsyncTask \- 2

@@

@Override
protected void done() \{
...
try \{
...

\} catch (InterruptedException e) \{
android.util.Log.w(.., e);
\} catch (ExecutionException e) \{
throw new RuntimeException("An error occured while executing doInBackground()",
e.getCause());
\} catch (CancellationException e)  \{
...
\} catch (Throwable t) \{
throw new RuntimeException("An error occured while executing "
+ "doInBackground()", t);
\}
...
\}
\}

@@

(java.lang.RuntimeException,java.lang.OutOfMemoryError) \- 30
(java.lang.RuntimeException,java.lang.NoClassDefFoundError) \- 6
(java.lang.RuntimeException,java.lang.UnsatisfiedLinkError) \- 5
(android.view.InflateException,java.lang.OutOfMemoryError) \- 4
(java.lang.RuntimeException,java.lang.StackOverflowError) \- 4

@@

APP	9
LIB	9
ANDROID	4

(com.octo.android.robospice.persistence.exception.CacheSavingException,java.lang.ClassCastException)	6
(java.lang.reflect.InvocationTargetException,java.lang.NullPointerException)	3
(java.lang.reflect.InvocationTargetException,android.content.res.ResourcesdNotFoundException)	2
(java.sql.SQLException,android.database.sqlite.SQLiteDiskIOException)	2
(java.lang.Exception,at.andiwand.odf2html.odf.IllegalMimeTypeException)	2

@@

ANDROID	5
APP	3

(java.lang.reflect.InvocationTargetException,java.lang.OutOfMemoryError)	5
(java.lang.Exception,java.lang.OutOfMemoryError)	1
(java.lang.reflect.InvocationTargetException,java.lang.NoSuchMethodError)	1
(java.lang.reflect.InvocationTargetException,java.lang.UnsatisfiedLinkError)	1

All wrappings except 1 were caused by the reflection library.

at java.lang.reflect.Constructor.constructNative(Native Method)
NATIVE IMPLEMENTATION, WE DO NOT HAVE ACCESS TO THE SOURCE CODE… IT IS IN C…
CHECKED EXCEPTIONS CAN BE THROWN BY NATIVE METHODS…. ANY CHANING IS PERFORMED?

In one of the cases, however, in project OpenDocument.droid a java.lang.Exception was 
wrapping a java.lang.OutOfMemoryError. General handlers are considered as bad practice, 
but wrapphing any exception on a general Exception make the matters worse.

@@

libcore	\- 3
 JAVA ENV \- 	4

(java.lang.NoClassDefFoundError,java.lang.ClassNotFoundException);4
(java.lang.AssertionError,javax.crypto.ShortBufferException);3

All ClassDefFound wrappings were caused by java.lang.Class methods such as 
at java.lang.Class.getDeclaredFields(Native Method)
at java.lang.Class.getDeclaredConstructors(Native Method). They are all NATIVE METHODS.

@@

APP	11
ANDROID	1
LIB	1

@@

@@

@@

>>>>

\subsubsection{Distiling Exception Stack Trace Information}

\- root exception

\- signaler
\- method
\- class
\- package

\- Exception

@@

 % SELECT id, exception, exception_extends, exception_from, exception_package, 
 %      issueid_onexminer, main_cause, main_extends, main_from, main_package, 
 %      main_pre_signaler_java, main_signaler, mainsignaler_class, mainsignaler_from, 
 %      mainsignaler_method, mainsignaler_package, pre_signaler_java, 
 %      repo, root_cause, root_extends, root_from, root_package, root_pre_signaler_java, 
 %      root_signaler, rootsignaler_class, rootsignaler_from, rootsignaler_method, 
 %      rootsignaler_package, signaler, signaler_class, signaler_from, 
 %      signaler_method, signaler_package, stack
 % FROM stacktracesummary;

@@

%\begin{figure}
%\centering
%\includegraphics[width=\hsize]{chart_exceptiontypes.pdf}
%\includegraphics[width=\hsize]{exception_types.pdf}
%\caption{Distribution of Checked and Unchedked exceptions.}
%\label{fig:typeroot}
%\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{llll}
    \hline
    \bfseries{Wrapper Type} & \bfseries{Root Cause} & \bfseries{Occurrences} & \bfseries{Projects} \\
    \hline
      %none   & Runtime   &  2360 & 359 \\
      %none  &   Checked  & 422  & 117 \\
      %none  &   Error   & 381  & 141 \\
      %none &  Undefined  &  15   & 10  \\
      %none & Throwable  &  1    & 1 \\
     %\hline
      %Runtime   & Runtime & 560  & 182 \\    
      %Checked   & Checked & 98   & 42  \\
      %Error     & Error   & 15   & 14  \\
    %\hline
      Runtime &  Checked   & 114  & 70  \\
      Runtime   &  Error   & 57   & 38  \\
      Checked &  Runtime   & 22   & 12  \\
      Checked & Error    &  8    & 7 \\
      Error & Checked     &  7    & 4 \\
      Error & Runtime     &  13   & 6 \\
      Throwable & Runtime &  3    & 1 \\
      %Undefined & Runtime &  3    & 3 \\
      %Undefined & Error &  1    & 1 \\
    \hline
  \end{tabular}
\caption{Kinds of wrappings found on the stacks of 482 ANDROID projects found on Github}
\label{tab:wrappingandroid}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{ll}
    \hline
    \bfseries{signaler from} & \bfseries{Ocurrences} \\
    \hline
ANDROID	 & 66 \\
APP	& 29 	(HOW MANY?? AND WHICH??) \\
LIB  & 19 (HOW MANY AND WHICH?)\\
\hline
  \end{tabular}
\caption{Elements responsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{ll}
 \bfseries{Signaler class} & \bfseries{Ocurrences} \\
    \hline
android.app.ActivityThread & 47 \\
android.view.LayoutInflater & 7 \\
org.gege.caldavsyncadapter.syncadapter.SyncAdapter & 7 \\
org.springframework.web.client.RestTemplate & 6 \\
android.os.AsyncTask & 5 \\
\hline
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

Code snipet extracted from android.app.ActivityThread.

{\footnotesize
\begin{verbatim}

private Activity performLaunchActivity(...) {
  try {
   ...
  } catch (Exception e) {
    ...
    throw new RuntimeException(..., e);
  }
}
\end{verbatim}
}

@@

\begin{table}
\centering
\begin{tabular}{lll}
    \hline
    \bfseries{wrapper} & \bfseries{root} & \bfseries{\#} \\
    \hline
java.lang.RuntimeException & java.lang.ClassNotFoundException &	32 \\
java.lang.RuntimeException & java.lang.NoSuchMethodException &	6 \\
java.lang.RuntimeException & java.lang.InstantiationException) & 5 \\
...andlyticsproject.NetworkException & org.apache...HttpResponseException &	5\\
android.view.InflateException & java.lang.NoSuchMethodException & 4 \\
\hline
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

\begin{table}
\centering
\begin{tabular}{lll}
    \hline
    \bfseries{Exception} & \bfseries{Ocurrences} \\
    \hline
java.lang.RuntimeException &	69 & 61\% \\
android.view.InflateException	& 10 & 8,7\% \\
com.github.andlyticsproject.console.NetworkException	& 7 & - \\
java.lang.IllegalStateException	& 6 & - \\

\hline
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{ll}
 \bfseries{Signaler from} & \bfseries{Ocurrences} \\
    \hline
ANDROID	& 50 \\
LIB  & 6 \\
APP	& 1 \\
\hline
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

\begin{table}
\centering
\begin{tabular}{ll}
 \bfseries{Signaler method} & \bfseries{Ocurrences} \\
    \hline
android.os.AsyncTask &	25 \\
android.app.ActivityThread & 15 \\
android.view.LayoutInflater & 7 \\
org.asynctasktex.AsyncTaskExd & 3 \\
android.support.v4.content.ModernAsyncTask & 2\\
\hline
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

@@

{\footnotesize
\begin{verbatim}
protected void done() {
 ...
   try {
      ...
   } catch (InterruptedException e) {
      android.util.Log.w(..., e);
   } catch (ExecutionException e) {
      throw new RuntimeException("...",e.getCause());
   } catch (CancellationException e) {
      ...
   } catch (Throwable t) {
     throw new RuntimeException("...", t);
   }
    ...
 }
}
\end{verbatim}
}

@@

\begin{table}
\centering
\begin{tabular}{ll}
 \bfseries{Signaler method} & \bfseries{Ocurrences} \\
    \hline
java.lang.RuntimeException,java.lang.OutOfMemoryError & 30\\
java.lang.RuntimeException,java.lang.NoClassDefFoundError & 6\\
java.lang.RuntimeException,java.lang.UnsatisfiedLinkError) & 5\\
android.view.InflateException,java.lang.OutOfMemoryError) & 4\\
java.lang.RuntimeException,java.lang.StackOverflowError)  & 4\\
\hline
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{ll}
 \bfseries{Origin} & \bfseries{Ocurrences} \\
    \hline
APP	& 9 \\
LIB	& 9 \\
ANDROID &	4 \\
\hline
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}
\begin{table}
\centering
\begin{tabular}{lll}
 \bfseries{Wrapper} & \bfseries{Root} & \bfseries{Ocurrences}\\
 \hline
...android.robospice.CacheSavingException,java.lang.ClassCastException & 6 \\
java.lang.reflect.InvocationTargetException,java.lang.NullPointerException &  3 \\
java.lang.reflect.InvocationTargetException,android...ResourcesdNotFoundException & 2 \\
java.sql.SQLException,android.database.sqlite.SQLiteDiskIOException & 2 \\
java.lang.Exception,at.andiwand.odf2html.odf.IllegalMimeTypeException & 	2 \\
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{ll}
 \bfseries{Origin} & \bfseries{Ocurrences} \\
    \hline
ANDROID	& 5 \\
APP	& 3 \\
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

\begin{table}
\centering
\begin{tabular}{lll}
 \bfseries{Wrapper} & \bfseries{Root} & \bfseries{Ocurrences}\\
 \hline
java.lang.reflect.InvocationTargetException,java.lang.OutOfMemoryError & 5 \\
java.lang.Exception,java.lang.OutOfMemoryError & 1 \\
java.lang.reflect.InvocationTargetException,java.lang.NoSuchMethodError &	1 \\
java.lang.reflect.InvocationTargetException,java.lang.UnsatisfiedLinkError&	1 \\
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

All wrappings except 1 were caused by the reflection library.
The method responsible for the wrappings (e.g., at java.lang.reflect.Constructor.constructNative(Native Method))
were native methods written in C. In one of the cases, however, in project OpenDocument.droid a java.lang.Exception was 
wrapping a java.lang.OutOfMemoryError. General handlers are considered as bad practice, 
but wrapping an Error on a general Exception make the matters worse.

@@

\begin{table}
\centering
\begin{tabular}{ll}
libcore	&  3 \\
 JAVA ENV  & 	4 \\
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

\begin{table}
\centering
\begin{tabular}{lll}
 \bfseries{Wrapper} & \bfseries{Root} & \bfseries{Ocurrences}\\
 \hline
java.lang.NoClassDefFoundError & java.lang.ClassNotFoundException & 4 \\
java.lang.AssertionError & javax.crypto.ShortBufferException) & 3 \\
 \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

Some wrappings were performed by methods defined by java.lang.Class methods such as 
at java.lang.Class.getDeclaredFields(Native Method)
at java.lang.Class.getDeclaredConstructors(Native Method).  While were performed by javax.crypto package.

@@

\begin{table}
\centering
\begin{tabular}{ll}
APP & 11 \\
ANDROID	& 1 \\
LIB	& 1 \\
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

\begin{table}
\centering
\begin{tabular}{lll}
 \bfseries{Wrapper} & \bfseries{Root} & \bfseries{Ocurrences}\\
 \hline
java.lang.ExceptionInInitializerError,java.lang.NullPointerException & 9 \\
java.lang.ExceptionInInitializerError,java.lang.IllegalArgumentException &	2 \\
java.lang.ExceptionInInitializerError,java.util.MissingResourceException) &	1 \\
java.lang.ExceptionInInitializerError,org.andengine.util.exception.AndEngineRuntimeException &	1 \\
 \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

after manually inspecting the code associated to such wrappings we discovered that all of them were 
caused by static initializers. If any exception is thrown in the context of a static initializer (i.e., static block) 
it is converted into an ExceptionInitializerError on the point where the class is first used.

@@

\subsubsection{Multiple Wrappings}

@@

\subsection{Checked and Unchecked Exceptions in JVM and Android and what they can tell us?}

We could observe that some of the type-changing-wrappings were performed by JDK classes.
Such finding lead us to think that the exception types have been used as intercheagable and may not being carrying 
the meaning they were firstly designed to carry.

The way the exceptions are being handle are more important that the type itself, it points to the fact already discussed 
by other languages such as M\# blog [ref] and \"thinking in Java author\" and other blogs. It is all about the exception handling
politics of a system and not the type itself. The exception type is not enought to ensure a more strict or robust development,
since the checked exceptions may be silienced or converted to a checked exception. According to Java manual,
they say that it can actually happen but it will be done intentionally and they advocate that it is a bad practice.

Present the number of checke and unchecked exceptions in JVM, JDK, Android SO, and Android SDK.
Discuss about the amount of checked and unchecked defined in each, and discuss about interesting exceptions that
have the same name ex: classNotFound...

\subsection{Top Signalers and what they can tell us?}

Present the top signalers found in this study, and top pairs (signalers and exceptions), and discuss 
about inversion of control and the difficult to adequately handle exceptions in this style of development.
Inversion of control stimulate the use of unchecked exceptions since the "call back" do not know which exception to expect.

{\tiny
\begin{verbatim}

%SELECT (mainsignaler_method, main_cause), count(distinct(repo)) as n
%  FROM stacktracesummary group by (mainsignaler_method, main_cause) order by n desc;

GITHUB:
"(dalvik.system.BaseDexClassLoader.findClass,java.lang.ClassNotFoundException)";19
"(android.app.Instrumentation.checkStartActivityResult,android.content.ActivityNotFoundException)";17
"(android.graphics.BitmapFactory.nativeDecodeStream,java.lang.OutOfMemoryError)";16
"(android.os.Parcel.readException,java.lang.SecurityException)";16
"(android.view.WindowManagerImpl.findViewLocked,java.lang.IllegalArgumentException)";14
"(android.graphics.BitmapFactory.nativeDecodeAsset,java.lang.OutOfMemoryError)";14
"(dalvik.system.PathClassLoader.findClass,java.lang.ClassNotFoundException)";13
"(android.support.v4.app.FragmentManagerImpl.checkStateLoss,java.lang.IllegalStateException)";12
"(android.graphics.Bitmap.nativeCreate,java.lang.OutOfMemoryError)";11

GOOGLECODE:
"(android.app.Instrumentation.checkStartActivityResult,android.content.ActivityNotFoundException)";8
"(dalvik.system.BaseDexClassLoader.findClass,java.lang.ClassNotFoundException)";6
"(java.lang.ClassLoader.loadClass,java.lang.ClassNotFoundException)";6
"(com.android.dx.dex.file.ClassDefsSection.add,java.lang.IllegalArgumentException)";6
"(android.graphics.Bitmap.nativeCreate,java.lang.OutOfMemoryError)";6
"(android.view.WindowManagerImpl.findViewLocked,java.lang.IllegalArgumentException)";5
"(android.graphics.BitmapFactory.nativeDecodeStream,java.lang.OutOfMemoryError)";5
"(junit.framework.Assert.fail,junit.framework.AssertionFailedError)";4
"(android.graphics.BitmapFactory.nativeDecodeAsset,java.lang.OutOfMemoryError)";4
"(dalvik.system.PathClassLoader.findClass,java.lang.ClassNotFoundException)";4

COMBINED:
"(dalvik.system.BaseDexClassLoader.findClass,java.lang.ClassNotFoundException)"; 25
"(android.app.Instrumentation.checkStartActivityResult,android.content.ActivityNotFoundException)";25
"(android.graphics.BitmapFactory.nativeDecodeStream,java.lang.OutOfMemoryError)";21
"(android.view.WindowManagerImpl.findViewLocked,java.lang.IllegalArgumentException)";19
"(dalvik.system.PathClassLoader.findClass,java.lang.ClassNotFoundException)";17
"(android.os.Parcel.readException,java.lang.SecurityException)";16
"(android.graphics.BitmapFactory.nativeDecodeAsset,java.lang.OutOfMemoryError)";14
"(android.support.v4.app.FragmentManagerImpl.checkStateLoss,java.lang.IllegalStateException)";12
"(android.graphics.Bitmap.nativeCreate,java.lang.OutOfMemoryError)";11

%SELECT (mainsignaler_class, main_cause), count(distinct(repo)) as n
 % FROM stacktracesummary group by (mainsignaler_class, main_cause) order by n desc;

GITHUB:
"(android.graphics.BitmapFactory,java.lang.OutOfMemoryError)";27
"(dalvik.system.BaseDexClassLoader,java.lang.ClassNotFoundException)";19
"(android.content.res.Resources,android.content.res.ResourcesdNotFoundException)";18
"(android.app.Instrumentation,android.content.ActivityNotFoundException)";17
"(libcore.io.Posix,libcore.io.ErrnoException)";17
"(android.os.Parcel,java.lang.SecurityException)";16
"(android.app.ActivityThread,java.lang.RuntimeException)";15
"(android.support.v4.app.FragmentManagerImpl,java.lang.IllegalStateException)";14
"(android.view.WindowManagerImpl,java.lang.IllegalArgumentException)";14
"(android.graphics.Bitmap,java.lang.OutOfMemoryError)";13
"(dalvik.system.PathClassLoader,java.lang.ClassNotFoundException)";13
"(android.os.Parcel,java.lang.NullPointerException)";12
"(android.support.v4.app.Fragment,java.lang.IllegalStateException)";11

GOOGLECODE:
"(android.app.Instrumentation,android.content.ActivityNotFoundException)";8
"(android.graphics.BitmapFactory,java.lang.OutOfMemoryError)";7
"(android.app.ActivityThread,java.lang.RuntimeException)";7
"(java.lang.ClassLoader,java.lang.ClassNotFoundException)";6
"(dalvik.system.BaseDexClassLoader,java.lang.ClassNotFoundException)";6
"(android.graphics.Bitmap,java.lang.OutOfMemoryError)";6
"(com.android.dx.dex.file.ClassDefsSection,java.lang.IllegalArgumentException)";6
"(android.view.WindowManagerImpl,java.lang.IllegalArgumentException)";5
"(android.database.sqlite.SQLiteDatabase,android.database.sqlite.SQLiteException)";4
"(android.os.Parcel,java.lang.IllegalArgumentException)";4

COMBINED:
"(android.graphics.BitmapFactory,java.lang.OutOfMemoryError)"; 34
"(dalvik.system.BaseDexClassLoader,java.lang.ClassNotFoundException)"; 27
"(android.content.res.Resources,android.content.res.ResourcesdNotFoundException)";18
"(android.app.Instrumentation,android.content.ActivityNotFoundException)";25
"(libcore.io.Posix,libcore.io.ErrnoException)";17
"(android.os.Parcel,java.lang.SecurityException)";20
"(android.app.ActivityThread,java.lang.RuntimeException)"; 22
"(android.support.v4.app.FragmentManagerImpl,java.lang.IllegalStateException)";14
"(android.view.WindowManagerImpl,java.lang.IllegalArgumentException)";19
"(android.graphics.Bitmap,java.lang.OutOfMemoryError)";19
"(dalvik.system.PathClassLoader,java.lang.ClassNotFoundException)";13
"(android.os.Parcel,java.lang.NullPointerException)";12
"(android.support.v4.app.Fragment,java.lang.IllegalStateException)";11

PACKAGE:

GITHUB:
"(android.graphics,java.lang.OutOfMemoryError)";35
"(dalvik.system,java.lang.ClassNotFoundException)";32
"(android.os,java.lang.RuntimeException)";27
"(android.support.v4.app,java.lang.IllegalStateException)";27
"(android.view,java.lang.IllegalArgumentException)";26
"(android.database.sqlite,android.database.sqlite.SQLiteException)";24
"(libcore.io,libcore.io.ErrnoException)";20
"(android.widget,java.lang.NullPointerException)";19
"(android.graphics,java.lang.RuntimeException)";18
"(android.content.res,android.content.res.ResourcesdNotFoundException)";18

GOOGLECODE:
"(android.os,java.lang.RuntimeException)";9
"(android.app,java.lang.RuntimeException)";9
"(android.app,java.lang.NullPointerException)";9
"(android.graphics,java.lang.OutOfMemoryError)";9
"(android.app,android.content.ActivityNotFoundException)";8
"(dalvik.system,java.lang.ClassNotFoundException)";8
"(android.view,java.lang.IllegalArgumentException)";7
"(java.lang,java.lang.ClassNotFoundException)";7
"(android.app,java.lang.IllegalArgumentException)";7
"(android.database.sqlite,android.database.sqlite.SQLiteException)";6

% SELECT mainsignaler_method,count(distinct(repo)) as n, string_agg(distinct(main_cause), ',')
% FROM stacktracesummary group by (mainsignaler_method) order by n desc;

GITHUB:
"android.os.Parcel.readException";28;"java.lang.IllegalArgumentException,java.lang.IllegalStateException,java.lang.NullPointerException,java.lang.SecurityException"
"dalvik.system.BaseDexClassLoader.findClass";19;"java.lang.ClassNotFoundException"
"android.app.Instrumentation.checkStartActivityResult";17;"android.content.ActivityNotFoundException"
"android.graphics.BitmapFactory.nativeDecodeStream";16;"java.lang.OutOfMemoryError"
"android.view.WindowManagerImpl.findViewLocked";15;"java.lang.IllegalArgumentException"
"android.graphics.Bitmap.nativeCreate";15;"java.lang.IllegalArgumentException,java.lang.OutOfMemoryError"
"android.graphics.BitmapFactory.nativeDecodeAsset";14;"java.lang.OutOfMemoryError,java.lang.RuntimeException"
"dalvik.system.PathClassLoader.findClass";13;"java.lang.ClassNotFoundException"
"android.support.v4.app.FragmentManagerImpl.checkStateLoss";12;"java.lang.IllegalStateException"
"android.os.BinderProxy.transact";12;"android.os.DeadObjectException,android.os.TransactionTooLargeException,java.lang.RuntimeException"

GOOGLECODE:
"android.app.Instrumentation.checkStartActivityResult";8;"android.content.ActivityNotFoundException"
"android.graphics.Bitmap.nativeCreate";8;"java.lang.IllegalArgumentException,java.lang.OutOfMemoryError,java.lang.RuntimeException"
"java.lang.ClassLoader.loadClass";6;"java.lang.ClassNotFoundException,java.lang.IncompatibleClassChangeError,java.lang.UnsupportedClassVersionError"
"dalvik.system.BaseDexClassLoader.findClass";6;"ClassNotFoundException,java.lang.ClassNotFoundException"
"com.android.dx.dex.file.ClassDefsSection.add";6;"java.lang.IllegalArgumentException"
"android.os.Parcel.readException";6;"Exception,java.lang.IllegalArgumentException,java.lang.IllegalStateException,java.lang.NullPointerException,java.lang.SecurityException"
"android.view.WindowManagerImpl.findViewLocked";5;"java.lang.IllegalArgumentException"
"android.os.BinderProxy.transact";5;"android.os.DeadObjectException,android.os.RemoteException,android.os.TransactionTooLargeException,java.lang.RuntimeException,java.lang.SecurityException"
"android.app.ActivityThread.performLaunchActivity";5;"Error,java.lang.NullPointerException,java.lang.RuntimeException"
"android.graphics.BitmapFactory.nativeDecodeStream";5;"java.lang.OutOfMemoryError"

COMBINED:

\end{verbatim}
}

@@

\subsubsection{Ways of Preventing Odd Wrappings}
